PANCHANGE_analysis

### 2020-11-03 PANCHANGE_analysis.Rmd
finalised grroup subsets for prepan sensitivity analysis

@@

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```

>>>>

Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began. 
```{r subsample for pre-pan sensitivity analysis}
# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_3months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_3_months_numeric == 1 # Only participants who signed up between December 1st 2019 and March 1st 2020
  )

# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_6months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_6_months_numeric == 1 # Only participants who signed up between September 1st 2019 and March 1st 2020
  )

# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_9months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_9_months_numeric == 1 # Only participants who signed up between June 1st 2019 and March 1st 2020
  )

```

@@

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```
# GAD prepan: sensitivity
